Sequence Labeling for Gait Analysis using LSTM

### 2015-05-09 paper/paper.tex

% \usepackage[utf8]{inputenc}
% \usepackage[english]{babel} % English language/hyphenation
\usepackage{booktabs}
\usepackage{multicol}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\usepackage{float}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{url}

@@

\begin{figure}[H]
 \centering
 \includegraphics[scale=.31]{./figures/Test1_1Train1_2Compare.png}
 % Test1_1Train1_2Compare.png: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=
 \caption{Comparison of Miller vs. LSTM network for various training intervals, for dataset 1.}
 \label{fig:halfAndHalfTrials}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[scale=.45]{./figures/Test2_2Train2_1Compare.png}
 % Test1_1Train1_2Compare.png: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=
 \caption{Comparison of Miller vs. LSTM network for various training intervals, for dataset 2.}
 \label{fig:halfAndHalfUsers}
\end{figure}

\section{Conclusion and Future Work}
\label{sec:Conclusion and Future Work}
\subsection{Conclusions}
The results from our initial implementation of the LSTM network are promising. Compared to the baseline methods we used for comparison, we achieved less confusion (false positive and false negative rate) and similar or better accuracy, measured through bias and quadratic error. This is

>>>>

% \usepackage[utf8]{inputenc}
% \usepackage[english]{babel} % English language/hyphenation
\usepackage{booktabs}
\usepackage{multicol}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\usepackage{float}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{url}
\usepackage{svg}

@@

\begin{figure}[H]
 \centering
 \includegraphics[scale=.5]{./figures/Test1_1Train1_2Compare.png}
 % \includesvg[scale=.31]{./figures/Test1_1Train1_2Compare.svg}
 % Test1_1Train1_2Compare.png: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=
 \caption{Comparison of Miller vs. LSTM network for various training intervals, for dataset 1.}
 \label{fig:halfAndHalfTrials}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[scale=.5]{./figures/Test2_1Train2_2Compare.png}
  %\includesvg[scale=.4]{./figures/Test2_2Train2_1Compare.svg}
 % Test1_1Train1_2Compare.png: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=
 \caption{Comparison of Miller vs. LSTM network for various training intervals, for dataset 2.}
 \label{fig:halfAndHalfUsers}
\end{figure}

\section{Conclusion and Future Work}
\label{sec:Conclusion and Future Work}
\subsection{Conclusions}
The results from our initial implementation of the LSTM network are very encouraging. Compared to the baseline methods we used for comparison, we achieved less confusion (false positive and false negative rate) and similar or better accuracy, measured through bias and quadratic error. According to \cite{Miller2009},  is true that Miller's method was implemented in a slightly modified way (fixed window size), so that his resu
